---
title: "Oversikt"
author: "Lars Nygaard"
abstract: "Financial Portal."
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: false 
##    toc: true
##    toc_depth: 2
##    toc_float: true
##    number_sections: true
params:
  year: 2018
  region: Europe
  printcode: TRUE
---

```{js, echo=FALSE}
$('.title').css('color', 'darkred')
```

```{r options, echo=FALSE, warning=FALSE, message=FALSE}
library(knitr)
options(prompt = "R> ", digits = 4, 
        show.signif.stars = FALSE,
        gvis.plot.tag='chart')
```

Hello, Website!

For more information about simple R Markdown websites, please read the documentation at https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html.

Please also note that simple R Markdown sites are _not_ based on **blogdown**. They are probably good for websites with only a few Rmd documents. For larger-scale and more sophisticated websites (such as blogs), you may want to use **blogdown** instead: https://github.com/rstudio/blogdown.

# This is a plot
```{r, eval=FALSE}
library(trelliscopejs)
library(ggplot2)
library(gapminder)
qplot(year, lifeExp, data = gapminder) +
  xlim(1948, 2011) + ylim(10, 95) + theme_bw() +
  facet_trelliscope(~ country + continent, nrow = 2, ncol = 7, width = 300, path = ".")
```

```{r}
print(params$year)
print(params$region)
print(params$printcode)
```

```{r}
set.seed(2020)
x <- seq(0,100,by=0.5)
y <- (50-x)^2+rnorm(length(x),sd=100)
 
curvy <- data.frame(x,y)
 
 ggplot(curvy, aes(x,y)) + geom_line()
```


# Animage
```{r}
library(reactable)
mainTable <- data.table::fread("data/mainTable.csv")
reactable(mainTable, groupBy = "Exchange", paginateSubRows = TRUE)
```



