---
title: "Oversikt"
params:
  year: 2018
  region: Europe
  printcode: TRUE
---

Hello, Website!

For more information about simple R Markdown websites, please read the documentation at https://bookdown.org/yihui/rmarkdown/rmarkdown-site.html.

Please also note that simple R Markdown sites are _not_ based on **blogdown**. They are probably good for websites with only a few Rmd documents. For larger-scale and more sophisticated websites (such as blogs), you may want to use **blogdown** instead: https://github.com/rstudio/blogdown.

<script src="javascript.js"></script>
<script src="https://unpkg.com/trelliscopejs-lib/dist/trelliscope.min.js"></script>
<div id="8a43f2dd" class="trelliscope-not-spa" style="width:800px; height:500px;"></div>




# This is a plot
```{r}
library(trelliscopejs)
library(ggplot2)
library(gapminder)
qplot(year, lifeExp, data = gapminder) +
  xlim(1948, 2011) + ylim(10, 95) + theme_bw() +
  facet_trelliscope(~ country + continent, nrow = 2, ncol = 7, width = 300)
```

```{r}
forex <- data.table::fread("file.csv")
DT::datatable(forex)
print(params$year)
print(params$region)
print(params$printcode)
```

# Interactive plot

```{r}
tmap_mode("view")

tm_shape(World) +
    tm_polygons("HPI")
```


<script>
  (function() {
    trelliscopeApp('8a43f2dd',
      'http://hafen.github.io/trelliscopejs-demo/housing/appfiles/config.jsonp');
  })();
</script>